---
title: "`r paste0(country, ' (', iso,')')`"
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Data and model fitting {.tabset}

## TB case notification data from WHO
```{r echo=FALSE, fig.height=3, fig.hold="hold", out.width="90%"}
gs$g_CNR
```

## TB prevalence survey data
```{r echo=FALSE, fig.height=5, fig.hold="hold", out.width="90%"}
gss$g_Prv
```

# Duration / Time to each state {.tabset}


<div class = "row">
<div class = "col-md-4">

#### Duration measures the time spent in a specific state
Where

 - **Asymptomatic TB**: from TB-detectable to symptom onset
 - **Symptomatic TB**: from symptom onset to notification

#### Time to state mearsures the time between detectable TB to a specific state


</div>
<div class = "col-md-8">
## Duration of each state
```{r echo=FALSE, fig.height=5, fig.hold="hold", out.width="90%"}
gs$g_Duration
```

## Time to each state
```{r echo=FALSE, fig.height=5, fig.hold="hold", out.width="90%"}
gs$g_TTE
```
</div>
</div>





# Healthcare cascade {.tabset}

<div class = "row">
<div class = "col-md-4">

#### Cascade can be defined by the proportion to the next stage

Dropouts can attributed to self-cure, background deaths, and untreated deaths


#### Cascade can consider the time-spent in each state

Longer duration in a state might related to a higher chance of dropout in care-seeking pathways.



</div>
<div class = "col-md-8">
## Proportions
```{r echo=FALSE, fig.height=4, fig.hold="hold", out.width="90%"}
gs$g_Cascade
```

## Time-spent
```{r echo=FALSE, fig.height=4, fig.hold="hold", out.width="90%"}
gs$g_Cohort_Total
```

## Time-spent by sex
```{r echo=FALSE, fig.height=7, fig.hold="hold", out.width="90%"}
gs$g_Cohort_Sex
```
</div>
</div>



